Robust DPG stability II

### 2012-03-26 docs/NewBCRobustness_paper/paper.tex
adding ta few small modifications to paper
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@394 36274a68-8941-4c93-80ef-affaed5139da

The estimates and proofs in this paper are largely based off of techniques and prior work done in \cite{DPGrobustness} and \cite{analysisDPG}; for further details, we encourage readers to consult these two publications as well.

@@

@@

>>>>

The estimates and proofs in this paper are largely based off of techniques and prior work done in \cite{DPGrobustness} and \cite{analysisDPG}; for further details, we encourage readers to consult these two publications as well.  The primary contributions in this paper are stability estimates for a new set of boundary conditions and a slightly different test norm.

@@

In each numerical experiment, we vary $\epsilon = .01, .001, .0001$ in order to demonstrate robustness over a range of $\epsilon$.  This is intended to mirror the numerical experiments in \cite{DPGrobustness}; for ``worst-case" linear solvers, such as LU decomposition without pivoting, the effect of roundoff error becomes evident for $\epsilon \leq O(1e-5)$.

\textcolor{red}{Add figure here on convergence for smaller epsilon}

@@

\pagebreak
